Generality in food webs scales with species richness, not latitude

### 2015-05-18 manuscript/latitudepaper.tex
not sure what I changed

>>>>

\section*{Abstract}

Several properties of food webs---the networks of feeding links between
species---vary systematically with the species richness of the underlying
community.  Under the ``latitude-niche breadth hypothesis'', which predicts
that species in the tropics will tend to evolve narrower niches, one might
expect that these scaling relationships could also be affected by latitude. To
test this hypothesis, we analysed the scaling relationships between species
richness and average generality, vulnerability, and links per species across a
set of 163 empirical food webs.  We also investigated scaling relationships
between the three food-web properties and the proportions of the web made up
by basal resources, intermediate consumers, and top predators. While we
observed no effect of latitude on scaling relationships in the estuarine,
marine, and terrestrial food webs, there were strong effects of latitude on
scaling relationships in the freshwater food webs. [[Need MUCH stronger justification for these... In lakes, this trend is
driven by increasing generality in high-latitude top predators while in
streams this trend appears to be driven by greater proportions of basal
resources in polar communities. Our results therefore provide partial support
the latitude-niche breadth hypothesis but also suggest that it may have
limited applicability in many empirical ecosystems. ]]
